### 2016-01-25 inputs/introduction.tex
intro-16:45

relatively recent genotyping technique alternative to SNP-chips that can 
be used to produce SNP genotype data~\cite{elshire_robust_2011}.

@@

sporadic missing genotypes: e.g., $\sim$52\% average in maize \cite{crossa_genomic_2013},
or up to 80\% for a fraction of SNPs in wheat \cite{poland_genomic_2012}. This 

>>>>

relatively recent technique which is considered a viable alternative to SNP array-based genotyping to produce SNP genotype data~\cite{elshire_robust_2011}.

@@

sporadic missing genotypes: e.g., $\sim$52\% and $\sim 58\%$ average in two maize experimental populations \cite{crossa_genomic_2013},
or ``up to 80\% missing data per marker'' in wheat \cite{poland_genomic_2012}. This 
